\section{Conclusion}
\label{hptpcPaper:sec:Conclusion}

The prototype High Pressure gas Time Projection Chamber was operated in the T10 beamline at CERN in August and September 2018 in order to make measurement of low momentum protons in argon.
The vessel was placed at a position off the axis of the beam, and a number of moderator blocks were placed directly in the beamline in order to reduce the average momentum of beam protons, reduce the flux and change the ratio of MIPs to protons off the beam axis.
\todo[inline]{JOCELYN: vague, rewrite to make this specific}
Measurements of the beam flux were made using two time of flight systems placed separately upstream and downstream of the TPC vessel.
\todo[inline]{JOCELYN: replace with numbers}
These measurements were used to determine the absolute and relative rates of protons and MIPS as well as their momenta, at different positions off the beam axis, and for varying numbers of moderator blocks.

\todo[inline]{JOCELYN: rewrite this paragraph-- no one cares what our expectation was before we measured... instead need to state what we measured and why we think it is correct!}
These measurements demonstrated that the unmoderated T10 beam was broader than originally anticipated, with a proton momentum range in line with the 0.8~GeV/c expected.
On adition of moderator blocks, the average momentum of protons reaching the TPC was reduced from 0.55-0.65~GeV/c with 0~moderator blocks to 0.30-0.45~GeV/c for 4 moderator blocks.
%The ratio of protons to MIPs was not uniformly increased as expected for a more focused beam.
While both the MIP and proton ratio were increased at off-axis positions, the overscattering of protons in the unexpectedly diffuse beam caused their increase in number to be smaller than that of the MIPs for some angles.
Given the number of particles observed by the downstream time of flight with 4~moderator blocks in the beamline, it is expected that [PROTON STEEL RESULT] protons per spill would reach the TPC active region with a momentum range of.

% classical summary/outlook
